Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
minor rewrite.

We thus  regard the  body of  the function as  an expression  tree and
consider paths from  the root of this tree to  the nodes corresponding
to the program points  which trigger evaluation---\SIF\ conditions and
\SRETURN\     expressions.      We     call    such     paths     {\em
  e-paths}.\footnote{Program  points  which   trigger  evaluation  are
  labelled with $\psi$. By an abuse of notation, we use the same label
  $\psi$ to refer  to the e-path terminating at a  point $\psi$.}  For
example, for the function \length, there  are three such paths $\epath_1 =
\langle  \pi_1, \pi_2,  \psi_1\rangle$, $\epath_2  = \langle\pi_1,  \pi_2,
\pi_3, \pi_4, \psi_2\rangle$ and $\epath_3  = \langle \pi_1, \pi_2, \pi_5,
\pi_6, \pi_7, \pi_8, \psi_3\rangle$.

>>>>

We thus  regard the  body of  the function as  an expression  tree and
consider paths from  the root of this tree to  the nodes corresponding
to the program points which trigger evaluation\footnote{Program points
  which      trigger      evaluation       are      labelled      with
  $\psi$.}---\SIF\ conditions and \SRETURN\ expressions.  We call such
paths {\em e-paths}.  For example, for the function \length, there are
three  such paths  $\epath_1 =  \langle \pi_1,  \pi_2, \psi_1\rangle$,
$\epath_2  = \langle\pi_1,  \pi_2,  \pi_3,  \pi_4, \psi_2\rangle$  and
$\epath_3  =  \langle  \pi_1,   \pi_2,  \pi_5,  \pi_6,  \pi_7,  \pi_8,
\psi_3\rangle$.
